\begin{questions}
\question{
Exact solution
}
\begin{solution}
The hamiltonian looks like this
\begin{equation}
  \begin{aligned}[b]
    H_U &= \Delta E \hat{n}_2 + U \hat{n}_{1\uparrow} \hat{n}_{1\downarrow} + U \hat{n}_{2\uparrow} \hat{n}_{2\downarrow} + (U-2J)\hat{n}_{1\uparrow} \hat{n}_{2\downarrow} \\
    &+ (U-2J)\hat{n}_{1\downarrow} \hat{n}_{2\uparrow}
  + (U-3J)\hat{n}_{1\uparrow} \hat{n}_{2\uparrow} + (U-3J)\hat{n}_{1\downarrow} \hat{n}_{2\downarrow} .
\end{aligned}
\end{equation}
The states that are going to yield a non-zero energy are $\ket{\uparrow,\downarrow}, \ket{\downarrow, \uparrow},$ $ \ket{\downarrow  \uparrow , 0} , \ket{0,\downarrow \uparrow}, \ket{\uparrow, \uparrow}, \ket{\downarrow, \downarrow} ,$ $ \ket{0,\downarrow}, \ket{0, \uparrow}$. Using the basis with this specific order we see
\begin{eqnarray}
  H_U \ket{\uparrow,\downarrow} = \Delta E + U- 2J,\\
  H_U \ket{\downarrow, \uparrow} =  \Delta E + U -2J,\\
  H_U \ket{\downarrow  \uparrow , 0} = U, \\
  H_U \ket{0,\downarrow \uparrow} = \Delta E + U,\\
  H_U \ket{\uparrow, \uparrow} = \Delta E+ U - 3J, \\
  H_U \ket{\downarrow, \downarrow} = \Delta E+ U - 3J,\\
  H_U \ket{0,\downarrow} = \Delta E,\\
  H_U \ket{0, \uparrow} = \Delta E.
\end{eqnarray}

So our matrix $H_U$ looks like
\begin{equation}
  \begin{pmatrix}
    \Delta E + U- 2J & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
    0& \Delta E + U- 2J & 0 & 0 & 0 & 0 & 0 & 0 \\
    0 & 0 & U & 0 & 0 & 0 & 0 & 0 \\
    0 & 0 & 0 & \Delta E + U & 0 & 0 & 0 & 0 \\
    0 & 0 & 0 & 0 & \Delta E+ U - 3J & 0 & 0 & 0 \\
    0 & 0 & 0 & 0&0 & \Delta E+ U - 3J & 0 & 0 \\
    0 & 0 & 0 & 0&0 & 0 & \Delta E & 0 \\
    0 & 0 & 0 & 0&0 & 0 & 0 & \Delta E\\
  \end{pmatrix}
\end{equation}
If we remember that the Hubbard model has the following form
\begin{equation}
  \begin{aligned}[b]
    H &= H_d + H_T + H_U \\
    & = \varepsilon \sum_i \sum_\sigma c_{i\sigma}^\dagger c_{i\sigma} - t \sum_{\langle ii'\rangle } \sum_\sigma c_{i\sigma}^\dagger c_{i'\sigma} + H_U
  \end{aligned}
\end{equation}
This turns into a complicated matrix. Luckily for us we just need to diagonalize $H_U$ and it's already diagonal. So the eigenstates is the basis we use to get this matrix form of the operator.\\

The ground state depends actually on some quantities, for example it depends on whether $ U - 3J $ is positive or negative. The ground state will be the eigenstate associated with the smaller diagonal terms. But if we suppose $U-3J<0$ then the ones with spins pointing in the same direction (5th and 6th row) $\ket{\uparrow, \uparrow}, \ket{\downarrow, \downarrow}$ have the smallest energies and their energies (coming from $H_U$) are going to be $\Delta E+ U - 3J$. So the ground state is going to be any linear combination of this two states.

If $\Delta E/J \rightarrow 0$ then $J\gg \Delta E$ so we can basically drop the $\Delta E$ term from the energy, for there are no qualitative changes. Maybe we can also ignore the last two terms because their energies are really small compared to the other ones.

If $\Delta E/J \rightarrow \infty$ then $J \ll \Delta E$ so we can drop the J terms and now we have a 5-fold degeneracy in the ground state. Now the states
$\ket{\uparrow,\downarrow}, \ket{\downarrow, \uparrow},$ $ \ , \ket{0,\downarrow \uparrow}, \ket{\uparrow, \uparrow}, \ket{\downarrow, \downarrow} ,$ have also the energy of the ground state, so any linear combination of this states it is going to be the ground state.
\end{solution}
\end{questions}
